---
title: "ggfocus -- for focus, people!"
author: "Dylan Stark"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ggfocus -- for focus, people!}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r header,echo=FALSE,results='hide'}
library("knitr")
opts_chunk$set(fig.width = 5.25, fig.height = 3.75, cache=FALSE)
```

```{r}
library(ggplot2)
library(ggfocus)
```

Sometimes you just want to emphasize some aspect of the data in your plot, such as the lack of low-depth fair diamonds.

```{r}
ggplot(diamonds, aes(depth, colour = cut)) +
  geom_density() +
  xlim(55, 70)
```

```{r}
ggplot(diamonds, aes(depth, colour = cut)) +
  geom_density() +
  xlim(55, 70) +
  scale_colour_focus(1)
```

As above, the plot doesn't necessarily need to be very "busy" to benefit from some focus.
Though, if it were busier, like the following 2-D density plot, the focus is more of a requirement in order to highlight an underlying trend.

```{r}
set.seed(4393)
dsmall <- diamonds[sample(nrow(diamonds), 1000), ]
ggplot(dsmall, aes(x, y)) +
  geom_density_2d(aes(colour = cut))
```

```{r}
ggplot(dsmall, aes(x, y)) +
  geom_density_2d(aes(colour = cut)) +
  scale_colour_focus(1)
```

```{r}
ggplot(dsmall, aes(x, y)) +
  geom_density_2d(aes(colour = cut)) +
  scale_colour_focus(1) +
  facet_wrap(~ cut)
```

```{r}
# http://ggplot2.tidyverse.org/reference/geom_boxplot.html
p <- ggplot(mpg, aes(class, hwy))
p + geom_boxplot(aes(colour = drv))
```

```{r}
p + geom_boxplot(aes(colour = drv)) +
  scale_colour_focus(2)
```



```{r}
	# http://ggplot2.tidyverse.org/reference/geom_jitter.html
	p + geom_jitter(aes(colour = class))
```

```{r}
	# http://ggplot2.tidyverse.org/reference/geom_jitter.html
	p + geom_jitter(aes(colour = class)) +
  scale_colour_focus(5)
```

```{r}
# http://ggplot2.tidyverse.org/reference/geom_path.html
	ggplot(economics_long, aes(date, value01, colour = variable)) +
  	  geom_line()
```

```{r}
# http://ggplot2.tidyverse.org/reference/geom_path.html
	ggplot(economics_long, aes(date, value01, colour = variable)) +
  	  geom_line() +
  scale_colour_focus(3)
```

```{r}
# http://ggplot2.tidyverse.org/reference/geom_smooth.html
	ggplot(mpg, aes(displ, hwy, colour = class)) +
  	  geom_point() +
  	  geom_smooth(se = FALSE, method = "lm")
```

```{r}
# http://ggplot2.tidyverse.org/reference/geom_text.html
p <- ggplot(mtcars, aes(wt, mpg, label = rownames(mtcars)))
p + geom_text(aes(colour = factor(cyl)))
```

Here we look at points and focus on only clarity of SI2.

```{r}
# http://ggplot2.tidyverse.org/reference/scale_brewer.html
	dsamp <- diamonds[sample(nrow(diamonds), 1000), ]
	(d <- ggplot(dsamp, aes(carat, price)) +
	  geom_point(aes(colour = clarity)))
```

Note that this doesn't necessarily help with overplotting.
The focus scale works also with tuning opacity and, as you'd expect, with jittering.

```{r}
# http://ggplot2.tidyverse.org/reference/scale_hue.html
	dsamp <- diamonds[sample(nrow(diamonds), 1000), ]
	d <- ggplot(dsamp, aes(carat, price, colour = clarity))
	d + geom_point(alpha = 0.2)
```

